Placing the spotted T Tauri star LkCa 4 on an HR diagram

### 2016-08-24 document/ms.tex
add existing coauthors
A stab at the conclusions, and cite the new Fang paper

\author{Michael A. Gully-Santiago,\altaffilmark{1} Gregory J. Herczeg,\altaffilmark{1} et al.}

\altaffiltext{1}{Kavli Institute for Astronomy and Astrophysics, Beijing, China}

@@

\section{Conclusions}
{\bf TBD}

>>>>

\author{Michael A. Gully-Santiago,\altaffilmark{1} Gregory J. Herczeg,\altaffilmark{1} Ian Czekala,\altaffilmark{2}, Garrett Somers\altaffilmark{2}, et al.}

\altaffiltext{1}{Kavli Institute for Astronomy and Astrophysics, Beijing, China}
\altaffiltext{2}{TBD}

@@

\section{Conclusions}
This paper has presented several complementary constraints on the photospheric properties of the weak-lined T-Tauri star LkCa 4, showing that this heavily spotted star was previously misplaced on the pre-main sequence HR diagram.  New results from \citet{fang2016} show that large starspot coverage fractions of $50\%$ are common among stars in the Pleiades.  LkCa 4 breaks the apparent trend of a ceiling at 50\% coverage fraction of cool starspots, though it is not yet clear how to classify stars for which the minority of the surface is purportedly the ambient photosphere.

Coupled with the results of \citet{fang2016} and \citet{covey16}, the results shown here suggest that the contribution of starspots to pre-main sequence stellar evolution have been systematically underestimated.  Large parts of the stellar surface are covered in spots that do not induce photometric modulation, either from circumpolar regions that always face towards our line-of-sight, longitudinally symmetric bands, or isotropic small spots.

The spectral inference technique described in this paper lays the foundation for future studies that seek accurate constraints on multiple photospheric components.  The near-IR has been shown to be the most sensitive region to search for cool emission from starspots.  Starspots and disk or accretion veiling can be modeled in this framework, and combining the two will enable studies of the large number of classical T-Tauri stars.  Applying this technique to large ensembles of T-Tauri stars across a wide range of mass and age will offer an observational picture of starspot evolution that can revise the current understanding of pre-main sequence stellar evolution.
